Concurrent Programming in Harmony

### 2022-01-23 book/paper.tex

Harmony, too, has a Hello World program.
\autoref{fig:helloworld} shows the program and the corresponding output.
From the command line, you can run it as follows:
\begin{code}
\begin{verbatim}
$ harmony -o hello1.png code/hello1.hny
\end{verbatim}
\end{code}
For this to work, make sure \texttt{harmony} is in your command shell's
search path.
The code for examples in this book can be found in the \texttt{code}
folder under the name listed in the caption of the example.
If you need to, you can download the sources separately from
\url{https://harmony.cs.cornell.edu/sources.zip}.
In this case, the file \texttt{code/hello1.hny} contains the
code in \autoref{fig:helloworld}.
The \texttt{-o hello1.png} arguments tell harmony to write the output
in the file \texttt{hello1.png}.
The output is a \emph{Deterministic State Machine} (DFA).  The green circle
represents the initial state and the double circle represents the final
state.  There is one \emph{transition}, labeled with the string
``hello world''.  The DFA describes (or \emph{recognizes}) all possible
outputs that the program can generate.  In this case, there is only one.

@@

The VSCode automatically updates to the latest version of Harmony when the extension is activated.
However, the update can also be directly prompted by using the Command Palette and running "Install Harmony".

>>>>

Harmony, too, has a Hello World program.
\autoref{fig:helloworld} shows the program and the corresponding output.
After installation (see \url{https://harmony.cs.cornell.edu}), you
can run it as follows from the command line:
\begin{code}
\begin{verbatim}
$ harmony -o hello1.png code/hello1.hny
\end{verbatim}
\end{code}
For this to work, make sure \texttt{harmony} is in your command shell's
search path.
The code for examples in this book can be found in the \texttt{code}
folder under the name listed in the caption of the example.
If you need to, you can download the sources separately from
\url{https://harmony.cs.cornell.edu/sources.zip}.
In this case, the file \texttt{code/hello1.hny} contains the
code in \autoref{fig:helloworld}.
The \texttt{-o hello1.png} arguments tell harmony to write the output
in the file \texttt{hello1.png}.
The output is a \emph{Deterministic State Machine} (DFA).  The green circle
represents the initial state and the double circle represents the final
state.  There is one \emph{transition}, labeled with the string
``hello world''.  The DFA describes (or \emph{recognizes}) all possible
outputs that the program can generate.  In this case, there is only one.

@@

The VSCode plug-in, developed by Kevin Sun and Anthony Yang,
is available from the VSCode market place: \url{https://marketplace.visualstudio.com/items?itemName=kevinsun-dev-cornell.harmonylang}.
This page comes with installation documentation.  VSCode also sports a
wonderful animator for Harmony output.

HarmonyLang is regularly updated to include the latest Harmony distribution.

\section{Harmony IDE for the cloud}

\texttt{Harmony IDE} is an Integrated Development Environment for Harmony,
also developed by Kevin Sun and Anthony Yang,
that runs in the cloud.  An important advantage of using \texttt{Harmony IDE}
is that you do not have to install anything.  You can even run in on your
smartphone.  However, since Harmony programs can use significant compute
resources, \texttt{Harmony IDE} must put a limit on the amount of compute
resources you can use.  So, while \texttt{Harmony IDE} is currently a great
way to try out Harmony, if you become a serious user of Harmony you
will probably want to install either the command-line version or
\texttt{HarmonyLang}.
\end{comment}
